\documentclass{cv-template}

\begin{document}

\cvheader{Elia Hilse}{%
  \href{mailto:elia@eliahilse.com}{elia@eliahilse.com}
  \quad$\cdot$\quad
  \href{https://linkedin.com/in/eliahilse}{\icon{linkedin} eliahilse}
  \quad$\cdot$\quad
  \href{https://x.com/eliahilse}{\icon{x} eliahilse}
  \quad$\cdot$\quad
  \href{https://github.com/eliahilse}{\icon{github} eliahilse}
  \quad$\cdot$\quad
  more context at \href{https://elia.vc}{elia.vc}%
}

\section{Education}

\entry{Dresden University of Technology}{Dresden, Germany}{B.Sc.\ in Applied Computer Science (paused for work)}{October 2023 -- Present}

\vspace{0.3em}

\entry{Konrad Adenauer Stiftung}{Scholarship, October 2023}{One of Germany's most competitive scholarships}{}

\vspace{0.3em}

\entry{Philipp-Melanchthon-Gymnasium}{Bautzen, Germany}{Graduated with 1.00 (845/900 / top 100 graduates nationwide)}{July 2023}

\section{Technical Skills}

\skillrow{Languages}{TypeScript, Python, C++, Rust, Java, C\#, PHP} \\
\skillrow{Technologies}{REST APIs, React/Svelte, AWS/GCP/Azure, MCP/Tools/Skills, Baremetal Infra, Distributed Systems, Realtime, Low-Latency, High-Availability} \\
\skillrow{Databases}{PostgreSQL, Apache Druid, (Apache Kafka), RocksDB, Clickhouse, (Redis), \ldots}

\section{Experience}

\entry{Instinct}{San Francisco, CA}{Founding Engineer}{Oct.\ 2025 -- Jan.\ 2026}
\vspace{0.1em}

Built all core platform primitives and frontend for the enterprise offering (Meta Ads but for UGC), e.g.:
\begin{tightlist}
  \item A double-entry ledger system processing \$300k+ in payouts and invoicing
  \item AI review pipelines re: posts, applications, task completion and payouts, enabling autonomous platform operation
  \item Near turing-complete automation service and event system (n8n-like), 150k+ invocations
  \item Organization and user profiling feeding into RAG (accurate retrieval @ 8M vectors)
  \item Horizontally scalable queue and container infra, real-time chat handling 20k+ simultaneously online users, and much more
\end{tightlist}
Architected the platform to effortlessly scale from 0 to 100k MAUs, 40M+ API requests and Terabytes of video data.

\vspace{0.4em}

\entry{Bilin GmbH}{Markkleeberg, Germany}{Principal Software Engineer, then Chief Technology Officer}{Aug.\ 2023 -- Sep.\ 2025}
\vspace{0.1em}

\begin{tightlist}
  \item Built BunkerCoin, a blockchain using a global short-wave radio-wave network mesh instead of the internet as transport layer. \$11M peak market cap. Received public endorsement by Anatoly Yakovenko, Solana Co-Founder.
  \item Built WonderCall (B2B Voice Agent, 500k minutes / 100k calls, 250ms e2e latency), B2C derivatives CreatorCall / DirtyCall, Token-Agnostic Payment Platform Aurion, and Elavos (AI Document \& Workflow platform) for the parent property company (\$30M AUM).
  \item Built the MVP on an exclusive content platform incl.\ custom DRM, tradeable creator rights, multi-level referrals and feature-parity with OnlyFans. Struck a dedicated High-Risk Master Processing Agreement with Visa and MasterCard.
\end{tightlist}

\vspace{0.4em}

\entry{Eternity}{Remote}{Founder}{Jan.\ 2023 -- May 2024}
\vspace{0.1em}

\begin{tightlist}
  \item Built a gaming data aggregation and NFT rental platform, at peak having 2k+ DAU and \$3M TVL
  \item Led an E-Sports team with \$70k in winnings across 20 Tournaments and a Content Creator Network
\end{tightlist}

\vspace{0.4em}

\entry{Previous Ventures}{Remote, see \href{https://elia.vc}{elia.vc}}{}{Jan.\ 2018 -- Jan.\ 2023}
\vspace{0.1em}

\begin{tightlist}
  \item Ran a tech YouTube channel, reaching 3M views total
  \item Built and sold physical Gaming PCs (50 in total)
  \item Built an SMM Panel, re-selling and providing botting services (followers/likes/views) for all major social media platforms. Peaked at 100k orders in a day.
\end{tightlist}

\section{Side Projects}

\entry{Hypervane}{Bash}{}{January 2026}
\vspace{0.1em}

Running one of the highest performing Solana Validators (Peak: Top 40, 1.0035 Slot Latency). Dark Fiber to Edge Routing in Equinix' FRA DC, direct peering with DE-CIX, 0.5ms RTT to GCP, AWS \& Jito, Tier 1 carriers (NTT), best hardware available (EPYC 9375F, 1TB RAM, 12TB Gen5 NVMe).

\vspace{0.4em}

\entry{Phantom}{TypeScript, Electron, Next}{}{July 2025}
\vspace{0.1em}

Built a chat outreach and management platform for agencies on exclusive content platforms, similar to Infloww but completely platform agnostic. Licensed to one of Germany's biggest exclusive content agencies for a \% of revenue. 2M+ messages handled across 12+ platforms.

\end{document}
